### 2017-11-08 README.Rmd
Update pkgdown
Add installation instructions

@@

#### Examples

@@

>>>>

# Installation

To install the current stable version of `infer`, make sure to install `devtools` first:

```
install.packages("devtools")
devtools::install_github("andrewbpray/infer")
```

To install the development version of `infer` (with `devtools` installed already):

```
devtools::install_github("ismayc/infer", ref = "dev")
```

@@

#### Randomization-based Examples

@@

Check the package vignettes for further examples using theory-based methods
in combination with randomization-based methods.
